Supplemental Information for\\``Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and subseasonal-to-seasonal predictive skill''

### 2018-05-06 reports/writeup/Supplement.tex
fix reference for CPC data
James edits of Angel comments
proposed james edits

@@

\begin{sidewaysfigure}
	\includegraphics[width=\textwidth, height=\textheight, keepaspectratio=true]{nino_sst_anomalies.pdf}
	\caption{
		Monthly SST anomalies during December of three major El Ni\~{n}o events.
		Months shown are NDJF of (a,d,g,j): 1982-83, (b,e,h,k): 1997-98, and (c,f,i,l): 2015-16.
		Units are in \si{\celsius}.
		SST data from \citet{Reynolds2002}.
		Also shown are rainfall anomalies over South America, from \citet{Xie2010}.
		Rainfall contour intervals are \SI{1}{\milli\meter\per\day}.
	}
\end{sidewaysfigure}

@@

>>>>

\begin{sidewaysfigure}
	\includegraphics[width=\textwidth, height=\textheight, keepaspectratio=true]{nino_sst_anomalies.pdf}
	\caption{
		Monthly SST anomalies during December of three major El Ni\~{n}o events.
		Months shown are NDJF of (a,d,g,j): 1982-83, (b,e,h,k): 1997-98, and (c,f,i,l): 2015-16.
		Units are in \si{\celsius}.
		SST data from \citet{Reynolds2002}.
		Also shown are rainfall anomalies over South America, from \citet{Chen2008}.
		Rainfall contour intervals are \SI{1}{\milli\meter\per\day}.
	}
\end{sidewaysfigure}

@@

@@

\begin{figure}
	\includegraphics[width=\textwidth]{predictors_eofs.pdf}
	\caption{
		Spearman (rank) correlation coefficient between several \gls{s2s} climate indices and weather type occurrence at monthly time step.
		These correlations are computed between the proportion of occurrence of each weather type and the monthly-mean time series of the climate index.
		For the \gls{mjo} phases the monthly-mean time series is the proportion of occurrence of that phase for the given month.
		The NINO 3.4 time series was up-sampled from monthly to daily values by persisting the most recent monthly value (no interpolation).
		The \acrfull{scad} predictor, labeled Dipole, is the mean meridional gradient of \gls{sst} anomalies over the region \SIrange{30}{10}{\degree W} and \SIrange{40}{15}{\degree S}, up-sampled to daily values using the same method as the NINO 3.4 time series.
	}\label{fig:predictor-eof}
\end{figure}
